Holomorphic field theories and higher algebra

### 2022-09-23 draft.tex
raised q about statement of duality
merge

\begin{dfn}
For a Lie algebra $\fg$, the {\em sphere algebra} in complex dimension $d$ is the dg Lie algebra~$\fg \otimes \sfA_d$.
Following \cite{FHK} we denote it by~$\fg^\bullet_d$.
\end{dfn}

@@

\begin{thm}[\owen{citations}]
The prefactorization algebra $\cF_A$ extends to a factorization algebra on $S^1$, and
\[
{\rm Hoch}_*(A) \simeq \check{C}(\mathfrak{U},\cF_A)
\]
for any Weiss cover of~$S^1$.
\end{thm}

@@

@@

We have already met the higher dimensional $\beta\gamma$ system on $\CC^n$.
This is an $n$-dimensional holomorphic system described by an $n$-dimensional translation invariant factorization algebra.
In part, the fields of this system constituted a holomorphic map $\gamma \colon \CC^n \to \CC^N$ together with its conjugate field $\beta$.

\brian{background on CDO's}

@@

\begin{rmk}
When $n=1$ we \cite{GGW} \brian{finish}
\end{rmk}

@@

This twist has a moduli-theoretic description that we now sketch;
we call a point in such a moduli space a {\it solution to the equations of motion}. 
(We give later a description in terms of fields and action functionals.)
Let $G_\CC$ denote the complex Lie group associated to $G$,
and let $\fg_\CC$ denotes its complex Lie algebra.

The twisted vector multiplet defines a field theory on any complex surface $X$ often called {\em holomorphic BF theory}. 
A solution encodes a holomorphic $G_\CC$-bundle $\cP \to X$ (by picking out a $\dbar$-connection on the underlying smooth bundle) and a holomorphic section of a shift of the adjoint bundle ${\mathrm ad}(\cP) \to X$.
\owen{rephrase the second part?}
The moduli space can be expressed as the mapping space ${\rm Map}(X, T^*[1]BG_{\CC})$, as a derived stack.

@@

A twisted matter multiplet also defines a field theory on any complex surface $X$. 
\owen{Is it a cotangent theory? It looks like a twisted cotangent theory.}
The superpotential determines a derived affine scheme: the derived critical locus ${\rm Crit}^d(W)$, which can be modeled as the spectrum of the dg algebra given by polyvector fields $PV(V)$ on $V$ with differential $\iota_{\d W}$.
(It is the Koszul complex associated to the Jacobi ring of $W$.)
This description makes manifest an odd symplectic structure on ${\rm Crit}^d(W)$,
as polyvector fields are an odd Poisson algebra via the Schouten bracket.
%As a dg space, the ring of functions of the derived critical locus is $\cO(\T^* [-1] V)$ equipped with the differential $\iota_{\d W}$. 
By itself (i.e., before coupling to a gauge theory) the twisted matter multiplet corresponds to the mapping space ${\rm Map}(X, {\rm Crit}^d(W))$.

Since $W$ is $G_\CC$-invariant, the critical locus has a residual Hamiltonian $G_\CC$-action. 
There is a version of Hamiltonian reduction for odd symplectic manifolds \cite{Pavel, Kevin, who else},
which we denote by ${\rm Crit}(W) \Sslash G_\CC$. 
\owen{I'm not sure we even need this.}
%As a dg space, the ring of functions is $\clie^\bu\big(\fg , \cO(\fg^* \oplus \Pi \T^* V) \big)$ where the differential is the Chevalley--Eilenberg differential plus $\iota_{\d W}$. 
The holomorphic twist of a theory with both vector and matter multiplets then corresponds to the  derived mapping space
\[
{\rm Map}(X , {\rm Crit}^d(W) \Sslash G_\CC), 
\]
which comes equipped with an odd symplectic structure. 
\owen{Should there also be a factor involving the $B$-fields of the BF gauge theory?}

@@

\begin{dfn}
A {\em holomorphic QCD theory} with $N$ {\em colors} and $F$ {\em flavors} is the holomorphic field theory on $\CC^2$ where
\begin{itemize}
\item the gauge fields are those of holomorphic BF theory valued in $\sl(N)$, whose fields are
\[
A \in \Omega^{0,\bu}(\CC^2 , \sl(N))[1] \quad\text{and}\quad B \in \Omega^{2,\bu}(\CC^2, \sl(N)^*);
\]
\item the ``quarks'' are fields of a holomorphic $\beta\gamma$ system valued in 
\[
V_Q = \Hom(\CC^F, \underline{N}) \cong \underline{N}^{\oplus F} \cong \CC^{NF},
\] 
whose fields are
\[
Q \in \Omega^{0,\bu}(\CC^2 , V_Q) \quad\text{and}\quad R \in \Omega^{2,\bu}(\CC^2 , V_Q^*)[1];
\]
\item the ``antiquarks'' are fields of a holomorphic $\beta\gamma$ system valued in the dual representation 
\[
V^*_Q \cong \Hom(\underline{N}, \CC^F) \cong (\underline{N}^*)^{\oplus F} \cong \CC^{NF}, 
\]
whose fields are
\[
Q^\dag \in \Omega^{0,\bu}(\CC^2 , V^*_Q) \quad\text{and}\quad R^\dag \in \Omega^{2,\bu}(\CC^2 , V_Q) [1].
\]
\end{itemize}
(The superscript $\dag$ does not mean we apply an operation to $Q$ or $R$; 
it is simply to remind us that these fields are the ``antiparticles''.)

The action functional is
\[
S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int r \,\dbar_A q,
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator. 
We will denote this theory by $\cT(N,F)$.\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.} 
\end{dfn}

@@

\begin{dfn}
A holomorphic QCD theory {\em with mesons}, denoted $\cT(N,F, V_M, W)$, is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
\[
M \in \Omega^{0,\bu}(\CC^2 , V_M) \quad\text{and}\quad N \in \Omega^{2,\bu}(\CC^2 , V_M^*) [1] .
\]
The action functional is
\[
S_{QCDwM} = S_{QCD} + \int N \,\dbar M + \int \d^2 z \; W(Q, \Tilde{Q}, M) .
\] 
\end{dfn}

@@

The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors, {\em without} mesons.
We denote it by~$\cT_{\sfE}(F, N)$.
We use $A, B, Q, R, Q^\dag$, and $R^\dag$ for the fields.

The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{M}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
(and $\check{L}$ for the partner field to $\check{M}$).
We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{M}  \check{Q}),$$
where we compose the linear maps before tracing over~$V_{\check{N}}$.
\end{dfn}

\owen{Please double-check that formula.}
%In this case the auxiliary vector space $Z$ is nontrivial (but transforms trivially under the gauge group as in the definition). 
%Our notation is $q,\Tilde{q}$ for elements of the vector spaces $V, \Bar{V}$ and $m\in Z$.
%The magnetic theory is
%\[
%\cT_{\sfM} (N_c, N_f) \define \cT\big(\SU(N_f - N_c) \, , \, (\CC^{N_f - N_c})^{\oplus N_f} \, , \, \CC^{\oplus N^2_f} \, , \, W = m q \Tilde{q} \big)
%\]
%In the definition of $W = m q \Tilde{q}$ we are using the natural contractions which we can describe explicitly as follows.
%Choose a basis $\{q_a^i\}$ for $V = (\CC^{N_f - N_c})^{\oplus N_f}$, $a = 1,\ldots, N_f - N_c$, $i=1,\ldots N_f$ and a dual basis $\{\Tilde{q}_i^a\}$ for $\Bar{V}$.
%Also, let $\{m_i^j\}$ be a basis for $\CC^{\oplus N_f^2}$. 
%Then the cubic polynomial $W$ is
%\[
%W = \sum_{i,j,a} m^i_j q_i^a \Tilde{q}^i_a .
%\]

@@

This claim should seem rather surprising.
In many ways these theories look, on their face, like very different theories:
the gauge groups $SL(N)$ and $SL(\check{N})$ are (usually) different, and
one side has mesons and the other does not.
But this feature also makes the conjecture powerful.

@@

Many stacks of interest to geometers and representation theorists appear naturally from holomorphic field theories.
For example, the holomorphic $\sigma$-model from $\CC^d$ into a target complex manifold $X$ has
\[
\cM_{\rm vac} \cong T^*[1-d]X.
\]
(If we consider the underlying underived stack, it is just $X$, unless $d = 1$.)
For supersymmetric gauge theories, the moduli stack of the holomorphic twist has the form
\[
\cM_{\rm vac} \cong V/G
\]
where $V$ is a (graded) $G$-representation and $V/G$ denotes the quotient stack.
The factor $V$ depends on the non-gauge fields (i.e., matter multiplets), which are sections of some associated vector bundle;
the quotient by $G$ arises from the gauge transformation.
For example, pure $\cN =1$ holomorphic Yang-Mills theory for group $G$ (i.e., the vector multiplet) has \owen{true?}
\[
\cM_{\rm vac} \cong \fg^*/G,
\]
the coadjoint quotient stack of the group.
(We are working in a $\ZZ/2$-graded world here.)
For general supersymmetric field theories, which involve both a $\sigma$-model and gauge fields, the holomorphic twist has a moduli stack of classical vacua of the form
\[
\cM_{\rm vac} \cong X/G
\]
where $X$ is a derived stack with a $G$-action and $X/G$ denotes the quotient stack.

In studying questions about the classical vacua of supersymmetric field theories, however, physicists have not typically worked with the {\em stack}.
Instead, they have worked with a GIT quotient.
For instance, in the setting of a gauge theory with moduli stack of classical vacua $V/G$, it means they work with
\[
V\Sslash G = \Spec(\cO(V)^G),
\]
the scheme whose ring of functions are the $G$-invariant functions on the representation~$V$.
This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
In practice physicists work ordinary schemes (i.e., without any derived directions), although one can also study the derived affine scheme that is the best approximation to a derived stack.
We will call this GIT quotient the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
(Note that the font of M changes between stack and space.)

@@

For the holomorphic QCD theory $\cT(F,N)$ without mesons, 
the moduli stack of classical vacua is 
\[
\cM_{\rm vac} \cong T^*[1] \left(V_Q \oplus V_Q^*)/SL(N)\right).
\]
By contrast the moduli space is a variety already well-studied in classical algebraic geometry.
The quark part of a vacuum lies on an $SL(N)$-orbit of $V_Q $, which consists of $F$ copies of the fundamental representation $\CC^N$, and likewise for the antiquark part.

\[
M_{\rm vac}(\cT) \cong ,
\]
the affine cone of a Grassmannian \owen{under Pl\"ucker embedding? need to check.} 
This result follows from classical invariant theory.
(
Identifying the $SL(N)$-invariant functions on $V_Q \oplus V^*_Q$ is one of the fundamental theorems of classical invariant theory.)
The moduli space for the magnetic theory is a bit more complicated but follows from invariant theory as well.

>>>>

\begin{dfn}[\cite{FHK}]
For a Lie algebra $\fg$, the {\em sphere algebra} in complex dimension $d$ is the dg Lie algebra~$\fg \otimes \sfA_d$.
We denote it by~$\fg^\bullet_d$.
\end{dfn}

@@

\begin{thm}[\owen{citations}]
The prefactorization algebra $\cF_A$ extends to a factorization algebra on $S^1$, and
\[
{\rm Hoch}_\bu(A) \simeq \check{C}(\mathfrak{U},\cF_A)
\]
for any Weiss cover of~$S^1$.
\end{thm}

@@

\subsection{Examples of holomorphic factorization algebras}

@@

A sheaf of chiral differential operators is a `chiralization' the familiar sheaf of differential operators on a complex manifold \cite{}.
It is a sheaf of vertex algebras $\CDO_X$ on a complex manifold $X$ which satisfies the property that under the Zhu construction one has an isomorphism of sheaves of associative algebras
\beqn
\text{Zhu}(\CDO_X) \simeq \cD_X
\eeqn
where $\cD_X$ is the sheaf of differential operators.

Unlike the sheaf of differential operators, one needs to fix additional data in order to define a sheaf of chiral differential operators. 
For a smooth complex manifold $X$, one of the main results of \cite{} is that the obstruction to the existence of such a sheaf is given by
\beqn
\ch_2(\T_X) \in H^{2}(X, \Omega^{2,cl}_X) 
\eeqn
and the space of all such algebras of chiral differential operators is a torsor for the group $H^{1}(X, \Omega^{2,cl}_X)$.
Here $\Omega^{2,cl}_X$ is the sheaf of closed holomorphic two-forms on $X$.

Locally, on an affine patch in $X$, the vertex algebra $\CDO_X$ is equivalent to $N$-copies of the familiar $\beta\gamma$ vertex algebra, where $N = \dim_\CC(X)$. 
We have seen that there is a natural generalization of the $\beta\gamma$ system to a holomorphic factorization algebra in any dimension.

@@

Anticipated by Witten, and proved in \cite{GGW}, the sheaf of chiral differential operators is given by the algebra of local operators of a familiar chiral CFT: the $\beta\gamma$ system of maps $\CC \to X$.
In this note, we have described a higher dimensional analog of this system as a holomorphic $\sigma$-model of maps $\CC^n \to X$. 
We have already met the higher dimensional $\beta\gamma$ system on $\CC^n$.
This is an $n$-dimensional holomorphic system described by an $n$-dimensional translation invariant factorization algebra.
In part, the fields of this system constituted a holomorphic map $\gamma \colon \CC^n \to \CC^N$ together with its conjugate field $\beta$. ''

@@

This twist has a moduli-theoretic description that we now sketch;
we call a point in such a moduli space a {\it solution to the equations of motion}. 
(We give later a description in terms of fields and action functionals.)
Let $G_\CC$ denote the complex Lie group associated to $G$,
and let $\fg_\CC$ denotes its complex Lie algebra.
We assume that $\fg_\CC$ is equipped with a non-degenerate symmetric invariant pairing and will freely identify $\fg_\CC$ with its linear dual using this data.

The twisted vector multiplet defines a field theory on any complex surface $X$ often called {\em holomorphic BF theory}. 
It will be convenient for us to assume that $X$ is equipped with a holomorphic volume form that we denote by $\Omega_X$. 
A solution encodes a holomorphic $G_\CC$-bundle $\cP \to X$ (by picking out a $\dbar$-connection on the underlying smooth bundle) and a holomorphic section of the adjoint bundle ${\mathrm ad}(\cP) \to X$.
The moduli space can be expressed as the mapping space ${\rm Map}(X, T^*[1]BG_{\CC})$, as a derived stack.
\brian{got rid of the term `shifted' section. Also, to write theory like this we use a CY structure, which I've now fixed.e}

@@

A twisted matter multiplet also defines a field theory on any complex surface $X$. 
\owen{Is it a cotangent theory? It looks like a twisted cotangent theory.}
\brian{right, $i_{dW}$ is the `twist'.}
The superpotential determines a derived affine scheme: the derived critical locus ${\rm Crit}^d(W)$ \brian{How do you feel about the notation $\RR \text{Crit}(W)$?}, which can be modeled as the spectrum of the dg algebra given by polyvector fields $PV(V)$ on $V$ with differential $\iota_{\d W}$.
(It is the Koszul complex associated to the Jacobi ring of $W$.)
This description makes manifest an odd symplectic structure on ${\rm Crit}^d(W)$,
as polyvector fields are an odd Poisson algebra via the Schouten bracket.
%As a dg space, the ring of functions of the derived critical locus is $\cO(\T^* [-1] V)$ equipped with the differential $\iota_{\d W}$. 
By itself (i.e., before coupling to a gauge theory) the twisted matter multiplet corresponds to the mapping space ${\rm Map}(X, {\rm Crit}^d(W))$.\footnote{Notice that AKSZ formalism equips this mapping space with a $1$-shifted symplectic structure as opposed to the desired $(-1)$-shifted symplectic structure.
Hereon we totalize all gradings to $\ZZ/2$.}

Since $W$ is $G_\CC$-invariant, the critical locus has a residual Hamiltonian $G_\CC$-action. 
There is a version of Hamiltonian reduction for odd symplectic manifolds \cite{Pavel, Kevin, who else},
which we denote by ${\rm Crit}(W) \Sslash G_\CC$. 
\owen{I'm not sure we even need this.} \brian{Probably if we want to cite a model for it, I think its fine to list the references here though.}
%As a dg space, the ring of functions is $\clie^\bu\big(\fg , \cO(\fg^* \oplus \Pi \T^* V) \big)$ where the differential is the Chevalley--Eilenberg differential plus $\iota_{\d W}$. 
The holomorphic twist of a theory with both vector and matter multiplets then corresponds to the  derived mapping space
\[
{\rm Map}(X , {\rm Crit}^d(W) \Sslash G_\CC), 
\]
which comes equipped with an odd symplectic structure. 
\owen{Should there also be a factor involving the $B$-fields of the BF gauge theory?}
\brian{That's already in this hamiltonian reduction. 
If $V$ is $(-1)$ shifted symplectic then I think the tangent space of $V \Sslash G$ should be
\beqn
\lie{g}[1] \oplus V \oplus \lie{g}^*[-2] .
\eeqn
Since we're forgetting to $\ZZ/2$ this is just $\Pi \lie{g} \oplus (V \oplus \lie{g})$.
}

@@

\begin{dfn}
A {\em holomorphic QCD theory} with $N$ {\em colors} and $F$ {\em flavors} is the holomorphic field theory on $\CC^2$ where
\begin{itemize}
\item the gauge fields are those of holomorphic BF theory valued in $\sl(N)$, whose fields are
\[
A \in \Omega^{0,\bu}(\CC^2 , \sl(N))[1] \quad\text{and}\quad B \in \Omega^{2,\bu}(\CC^2, \sl(N)^*);
\]
\item the ``quarks'' are fields of a holomorphic $\beta\gamma$ system valued in 
\[
V_Q = \Hom(\CC^F, \underline{N}) \cong \underline{N}^{\oplus F},
\] 
whose fields are
\[
Q \in \Omega^{0,\bu}(\CC^2 , V_Q) \quad\text{and}\quad R \in \Omega^{2,\bu}(\CC^2 , V_Q^*)[1];
\]
\item the ``antiquarks'' are fields of a holomorphic $\beta\gamma$ system valued in the dual representation 
\[
V^*_Q \cong \Hom(\underline{N}, \CC^F) \cong (\underline{N}^*)^{\oplus F}, 
\]
whose fields are
\[
q \in \Omega^{0,\bu}(\CC^2 , V^*_Q) \quad\text{and}\quad r \in \Omega^{2,\bu}(\CC^2 , V_Q) [1].
\]
\end{itemize}

The action functional is
\[
S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int r \,\dbar_A q,
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.
%We will denote this theory by $\cT(N,F)$.
\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.} 
\end{dfn}

@@

\begin{dfn}
A holomorphic QCD theory {\em with mesons}
%, denoted $\cT(N,F, V_M, W)$, 
is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
\[
M \in \Omega^{0,\bu}(\CC^2 , V_M) \quad\text{and}\quad N \in \Omega^{2,\bu}(\CC^2 , V_M^*) [1] .
\]
The action functional is
\[
S_{QCDwM} = S_{QCD} + \int N \,\dbar M + \int \d^2 z \; W(Q, \Tilde{Q}, M) .
\] 
Notice that to write down the superpotential term we are utilizing the holomorphic volume form $\Omega_X = \d^2 z$. 
\end{dfn}

@@

The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors, {\em without} mesons.
We denote it by~$\cT_{\sfE}(F, N)$.

The {\em magnetic theory} is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{M}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$ and with superpotential $$\check{W} =  \Tr(\check{q} \check{M}  \check{Q}),$$
where we compose the linear maps before tracing over~$V_{\check{N}}$.
We denote this theory by~$\cT_{\sfM}(F, \check{N})$.
\end{dfn}

%In this case the auxiliary vector space $Z$ is nontrivial (but transforms trivially under the gauge group as in the definition). 
%Our notation is $q,\Tilde{q}$ for elements of the vector spaces $V, \Bar{V}$ and $m\in Z$.
%The magnetic theory is
%\[
%\cT_{\sfM} (N_c, N_f) \define \cT\big(\SU(N_f - N_c) \, , \, (\CC^{N_f - N_c})^{\oplus N_f} \, , \, \CC^{\oplus N^2_f} \, , \, W = m q \Tilde{q} \big)
%\]
%In the definition of $W = m q \Tilde{q}$ we are using the natural contractions which we can describe explicitly as follows.
%Choose a basis $\{q_a^i\}$ for $V = (\CC^{N_f - N_c})^{\oplus N_f}$, $a = 1,\ldots, N_f - N_c$, $i=1,\ldots N_f$ and a dual basis $\{\Tilde{q}_i^a\}$ for $\Bar{V}$.
%Also, let $\{m_i^j\}$ be a basis for $\CC^{\oplus N_f^2}$. 
%Then the cubic polynomial $W$ is
%\[
%W = \sum_{i,j,a} m^i_j q_i^a \Tilde{q}^i_a .
%\]

@@

@@

Many stacks of interest to geometers and representation theorists appear naturally from holomorphic field theories.
For example, the holomorphic $\sigma$-model from $\CC^d$ into a target complex manifold $X$ has
\[
\cM_{\rm vac} \cong T^*[1-d]X.
\]
(If we consider the underlying underived stack, it is just $X$, unless $d = 1$.)
For supersymmetric gauge theories, the moduli stack of the holomorphic twist has the form
\[
\cM_{\rm vac} \cong V/G
\]
where $V$ is a (graded) $G$-representation and $V/G$ denotes the quotient stack.
The factor $V$ depends on the non-gauge fields (i.e., matter multiplets), which are sections of some associated vector bundle;
the quotient by $G$ arises from the gauge transformation.
For example, pure $\cN =1$ holomorphic Yang-Mills theory for group $G$ (i.e., the vector multiplet) has
\[
\cM_{\rm vac} \cong \fg^*/G,
\]
the coadjoint quotient stack of the group.
(We are working in a $\ZZ/2$-graded world here.)
Using the invariant pairing on $\fg$ we can further identify this with the adjoint quotient stack~$\fg / G$. 
For general supersymmetric field theories, which involve both a $\sigma$-model and gauge fields, the holomorphic twist has a moduli stack of classical vacua of the form
\[
\cM_{\rm vac} \cong X/G
\]
where $X$ is a derived stack with a $G$-action and $X/G$ denotes the quotient stack.

In studying questions about the classical vacua of supersymmetric field theories, however, physicists have not typically worked with the {\em stack}.
Instead, they have worked with a GIT quotient.
For instance, in the setting of a gauge theory with moduli stack of classical vacua $V/G$, it means they work with 
\brian{I don't like this notation, its confusing since it looks like symplectic reduction which has already appeared. 
What about $[V/G]$?}
\[
V\Sslash G = \Spec(\cO(V)^G),
\]
the scheme whose ring of functions are the $G$-invariant functions on the representation~$V$.
This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
In practice physicists work ordinary schemes (i.e., without any derived directions), although one can also study the derived affine scheme that is the best approximation to a derived stack.
We will call this GIT quotient the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
(Note that the font of M changes between stack and space.)

@@

For the holomorphic QCD theory with $F$ flavors and $N$ colors (without mesons), 
the moduli stack of classical vacua is 
\[
\cM_{\rm vac} \cong T^*[1] \left(V_Q \oplus V_Q^*)/SL(N)\right).
\]
By contrast the moduli space is a well-known variety, 
\[
M_{\rm vac}(\cT) \cong \Gr(F, N),
\]
the affine cone of a Grassmannian \owen{under Pl\"ucker embedding? need to check.} 
This result follows from classical invariant theory.
(The quark part of a vacuum lies on an $SL(N)$-orbit of $V_Q$, which consists of $F$ copies of the fundamental representation $\CC^N$, and likewise for the antiquark part.
Identifying the $SL(N)$-invariant functions on $V_Q \oplus V^*_Q$ is one of the fundamental theorems of classical invariant theory.)
The moduli space for the magnetic theory is a bit more complicated but follows from invariant theory as well.
